\documentclass[letterpaper,12pt]{memoir}
\usepackage[margin=1.00in]{geometry}
\usepackage{csquotes}
\usepackage[characterstyle={arden}]{thalie}
\usepackage{longtable}
\usepackage{tabu}
%\usepackage{pgfpages}

%\pgfpagesuselayout{2 on 1}[letterpaper,landscape]

\begin{document}
\begin{dramatis}
  \character[cmd=xishi,      desc=a character]{Xi Shi}
  \character[cmd=mengjiangnu,desc=a character whose personality is really sad]{Meng Jiang Nu}
  \character[cmd=zhinu,      desc=a character]{Zhi Nu}
  \character[cmd=niulang,    desc=a character]{Niu Lang}
  \character[cmd=host,       desc=a character]{Host}
  \character[cmd=niangniang, desc=a character]{Wang Mu Niang Niang}
\end{dramatis}


\scene{}

\disposablecharacter{Voiceover}
\textit{Previously on The Bachelor, we said goodbye to Hua Mulan as she left of her own accord to fight the Huns in her father's place. Though we were sad to see her go, you can see her featured in the upcoming feature film: Mulan.}

\host%
Tonight, we will see an end to this season of The Bachelor. Only 3 of the 30 beautiful women that appeared this season remain. Who will Niu Lang pick to be his beautiful wife? Will he find true love? Before we find out the answers to these hard-hitting questions, let's get a brief recap on the histories of our spectacular finalists.

\xishi%
Before I joined The Bachelor, everyone thought I was just another pretty face. I mean, they even sent me to distract emperor Fuchai with my beauty. Okay first of all, thanks for objectifying me. Second, if only the government had talked to me, then they'd realize that I am more than just a pretty face. I mean there even is a saying that my looks can drown fish! The only person who ever understood me was the scholar Fan Li, but we had to part ways because of my duty to my country. Now that the enemy is destroyed, I'm here on The Bachelor to fill the empty space in my heart Fan Li left. I miss him so much, but I've really enjoyed getting to know Niu Lang, and I really think he might be the first person after Fan Li to really get me.

\mengjiangnu%
You know, I had a really wonderful life before my husband left to build the Great Wall of China. That's when I lost everything. I was so devoted and loyal; I even knitted a blanket for him, but when I got there I found that he had passed away. I've never cried so much in my life. I thought I was going to drown in my tears. My family thought participating in this show might be a good idea because it would force me to get over my one true love, but I don't know. I'm really surprised I've made it this far. It's been hard to keep it together, but I'm really trying to not disappoint my family.

\zhinu%
As a heavenly weaver, I've seen my fair share of pretty cool guys, but I can honestly say that even though Niu Lang is a mortal and a cowboy, he's pretty cool. I guess this might sound kind of bad, but I kind of knew I would make it this far. I mean, I'm practically a fairy. What guy doesn't love a little fairy dust? Niu Lang has good judgment. I have faith that he will make the right decision for himself, and for me. I really just wanted to have fun on this show because it's an excuse for me to spend so much time on Earth. What's weird is that I think I might actually like Niu Lang.

\host%
Now that we've met all the contestants that are left, let's see what our bachelor Niu Lang has to say.

\niulang%
These few weeks have honestly been the best weeks of my life. Before appearing on this show, my sister in law kicked me out of the house. I was at a bad place in my life and was so lost. Now I have all these beautiful ladies interested in me. It's truly a miracle!


\scene{}
\onstage{!onstage directions! \niulangname{} and \xishiname{}}

\host%
Niu Lang seems to have picked the Lotus Garden to hang out with the girls and get to know them better.

\niulang%
I'm glad we get to spend some time together.

\xishi%
Likewise.

\niulang%
I've always been curious: What is something that you can't live without?

\xishi%
Well, I would say my beauty. Without my beauty I would not have been able to save China.

\niulang%
Oh wow! I had no idea you saved China. You were so soft-spoken throughout the whole show that I never knew you were a hero! What was it like to save China? How did you do it?

\xishi%
I was so beautiful that the emperor sent me to distract Fuchai so that the enemy could be taken down. The process was not easy. I had to make many sacrifices. I met a scholar when I was assigned to be a distraction. His name was Fan Li. We fell in love but we had to part ways because of my duties. \did{Trailing off, seeing Fan Li in the distance} He was so\dots

\niulang%
So what?! Don't keep me in suspense!

\xishi%
Oh my God, you should see for yourself! I think that's him right there! FAN LI!\@ IT'S ME!\@ XI SHI!\@ I'M OVER HERE!\@

\begin{dida}
  \xishiname{} runs to Fan Li. They reunite and start hugging. Niu Lang stares at the camera The Office style while \xishiname{} and Fan Li are in the background.
\end{dida}

\host%
It looks like \xishiname{} did the other girls a favor and eliminated herself from the show! Now \niulangname{} only has to choose between two beautiful women! Let's see how well he'll do with \mengjiangnuname!


\scene{}

\niulang%
Wow. This place is so pretty. It's so different from my farm back home.

\mengjiangnu[wiping a tear from her cheek]
Yes. It is pretty.

\niulang%
\mengjiangnuname, why are you always so sad?

\mengjiangnu%
It's kind of a long story. My husband, Fan Xi Lang, died you know. After searching for his body using my blood, I found his bones in the Great Wall of China. When I see beautiful places like this, I am reminded of the beauty surrounding the Great Wall and my husband's death. \did{She covers her face and cries.}

\niulang[looking uncomfortable]
Oh, okay. I'm sorry.

\begin{dida}
  Two soldiers walk up to the host who'd been standing on the side. They have a whispered conversation. The host turns back to the camera.
\end{dida}

\host%
Uh, sorry folks and sorry \niulangname{}. It looks like \mengjiangnuname{} is going to have to leave with these gentlemen here. \did{Pointing to the soldiers.} But never fear. She is not in any trouble. In fact, as a viewer of this show, the Emperor of China---the literal emperor of China (Qin Shi Huang)---saw Meng Jiang Nu's beauty as a qualification to be his own wife, so that's why Meng Jiang Nu is leaving. We are obviously sad to see her go, but the emperor‘s palace is definitely a step up from Niu Lang's farm, no offense Niu Lang. We wish you all the best, and I hope to see an invitation to the wedding in the mail!

\begin{dida}
  The soldiers march off with \mengjiangnuname.
\end{dida}

\niulang[in the reality TV confession cam thing FIXME] % FIXME
Well, I don't really have much of a choice now I guess, but it's okay. I like Zhi Nu a lot, and I'm sure that she will be a good wife. Unlike the other contestants, she's never left me, so I know that she will be a faithful and loyal wife.


\scene{}

\begin{dida}
  \zhinuname{} walks up to Niu Lang for their date.
\end{dida}

\zhinu%
Hello Niu Lang.

\niulang%
Hi Zhi Nu.

\zhinu%
Are you okay? You look sort of distracted and distant.

\niulang%
Yeah. I'm okay. I just don't know what to say or how to start. When I first met you, I was very unsure of myself. Heck, when I first came onto this show I was really unsure of myself. I'm just a poor cow herd, without anything special. The last bachelor on this show was emperor Qin Shi Huang Di for pete's sake, how on earth could I compete with that? But getting to meet you and spend time with you on this show has given me more confidence and happiness that I could have imagined.

\zhinu[in a confession cam]
Yes! This means he's going to pick me! I get to stay on Earth longer and I get to be with my one true love. I knew that this show was a good idea. I just hope that \niangniangname{} doesn't watch \textit{The Bachelor}. If she \textbf{(or he?)} does, then she'll \textbf{(or he'll)} be able to find me so easily, and the life that I'm just about to begin with Niu Lang will be over.

\niulang%
On that note, Zhi Nu, I want to give you my final rose and ask that you make me the happiest man alive for the rest of our lives by marrying me\dots so, what do you say?

\zhinu[embracing \niulangname]
Of course! I would love to!

\host%
And with that, ladies and gentlemen, we see a beautiful, happy ending to this season of \textit{The Bachelor}. Be sure to stick around, however, for \textit{The Bachelor: After the Final Rose}.


\scene{\textit{The Bachelor: After the Final Rose}}

\begin{dida}
  The \hostname{} is facing the audience with \niulangname{} and \zhinuname{} in the background. \zhinuname{} is seen holding a baby in her arms.
\end{dida}

\host[walking to meet \niulangname{} and \zhinuname{}]
Hello everyone, this is \textit{The Bachelor: After the Final Rose}, and we're back with everyone's favorite traditional Chinese couple, \niulangname{} and \zhinuname{}, contestants on season 1 of \textit{The Bachelor}. \niulangname{} and \zhinuname{} have kindly invited us back for just one week, to get a look into their lives, 5 years after the show's finale.

\niulang[in confession cam]
I really just love her. Our lives are simple, but I like it. I herd my cows and work on the farm. \zhinuname{} raises the children and tends to her weaving. She cooks and cleans the food that I bring home. It's all very good and well.

\zhinu%
It's really crazy that we've come so far. It is so strange to think that a little over 5 years ago, I was literally in heaven, and \niulangname{} was a simple cow herd. He still is a cow herd, but now I'm in figurative heaven because we have found love together, and we have a baby who is our pride and joy. I can't imagine anything more perfect, and we are both so happy. With children, I don't have as much time for my weaving, but I am content spending time with my kids and my husband on earth. I am still amazed that \niulangname{} hasn't discovered that I'm a fairy. I mean, I said it so many times on \textit{The Bachelor}, but he refuses to watch it. He doesn't like to see himself on screen.

\zhinu[walking towards the living room]
I can show you around the house a little bit. This is the kitchen. \did{Walking towards the living room.} This is the living room. \did{Walking towards the bathroom.} This is the--- AH!\@

\begin{dida}
  \niangniangname{} walks out of a door, into the room.
\end{dida}

\niangniang%
Yeah, that's right. Be afraid. How could you just abandon us in heaven and neglect your duties?  I am disappointed in you, \zhinu. You are embarrassing, you really are. You have been gone for almost 6 years. Did you think we wouldn't notice? Do you think we're stupid?! And who is this man that you supposedly married? What were you thinking? He cannot live in heaven with you. He is not immortal. It is impossible. A silly mistake by a young girl.

\zhinu%
\niangniangname{}, stop! I can explain. I love him.

\niangniang%
LOVE?! What do you know about love? You have no experience with love. You are coming back to heaven with me right now.

\zhinu%
No! I'm not. I'm staying here with \niulangname{}!

\niangniang%
You're coming with me if it's the last thing you do. Let's go.

\zhinu%
Wait! Can't I at least say goodbye first? Please. He won't know where I've gone. He'll be devastated. Please.

\niangniang[gesturing towards the \hostname{}]
This nice gentlemen over here will be able to tell your \enquote{beloved} everything. It's all recorded on that camera over there. He will get over it. We are going. Now.

\zhinu[crying]
No! Let me go! I have two kids that I need to take care off! Please!

\niangniang%
You are a fairy from Heaven! How dare you marry a cowboy from Earth! You shall never see you children and your husband again! \did{She throws her golden hairpin to summon a river across the sky.} This river will stop you two from ever seeing each other again! Now stay in heaven where you belong.

\zhinu[yelling]
Why can't you understand that we love each other?

\begin{dida}% FIXME
  They go back to heaven. Not sure exactly how yet. The \hostname{} stands up and regains composure. FIXME
\end{dida}

\host%
Well folks, it looks like we will see \niulangname{} back on \textit{The Bachelor} next season, for a second chance at true love. Stay tuned and thanks for watching!

\scene{Extra? FIXME} % FIXME

\disposablecharacter{Voiceover}
Well, let's view what happened to our earlier contestants! Did they find love in the end? Let's find out.

After finding her true love Fan Li once again, \xishiname{} lived in obscurity despite being the most beautiful woman in Chinese history and saving her country. Fan Li retired from his ministerial post and lived with \xishiname{} on a fishing boat. No one ever saw them again, but it is certain that they lived happily ever after.

After being taken forcibly off the show by the emperor, \mengjiangnuname{} agreed to marry him provided that a festival 49 days long is held in honor of her deceased husband and that the emperor and his officials are present at his burial. However, after Qin Shi Huang agreed to her requests, \mengjiangnuname{} insulted and cursed him for all the burdens and hardships he placed on the young men drafted to build the Great Wall. Remaining true to her love of her husband, she drowned herself in the river.

After \zhinuname{} was sent back to heaven, \niulangname{} and \zhinuname{} watch each other from afar, unable to reach one another. After seeing them in such despair, the magpies pity them once a year. On Qi Xi Jie, they form a bridge, so the star-crossed lovers can see each other. This true and heartwarming love of waiting to be reunited once a year became celebrated by many Chinese couples, forming modern-day Chinese Valentine's Day.

\end{document}

