\documentclass[letterpaper,12pt]{article}
\usepackage[margin=1.00in]{geometry}
\usepackage{csquotes}
\usepackage[characterstyle={imprimerie-verse}]{thalie}

\setlength{\parindent}{0pt}

\begin{document}
\begin{titlepage}
  \vspace*{\fill}
  {\Huge \textbf{{Checking Out}}}

  \vspace{1em}
  An original two-person short scene based on Vladimir Nabokov's \textit{Lolita}.

  \vspace{2em}

  Xinhui Xu (27) and Jeffrey Lin \\
  Mr.\ Mott \\
  British Literature, Period 1

  \vspace{3em}

  \vspace*{\fill}
\end{titlepage}

\begin{center}
  \textit{Humbert manages to fool people into thinking that he is an overly protective father.}
\end{center}


\begin{dramatis}
  \begin{center}
    \LARGE{\textsc{Dramatis Person\ae}}
  \end{center}

  \character[cmd=hum, drama=\textsc{Humbert}, desc=a literature professor who is guardian to Dolores Haze (Lolita).]{Humbert}
  \character[cmd=custodian, drama=\textsc{Custodian}, desc=a curious lady working in a hotel.]{Custodian}
\end{dramatis}

\begin{center}
  \LARGE{\textsc{Scene}}
\end{center}

\begin{dida}
  One morning at The Enchanted Hunters, Humbert rushes back to his room to find a janitor picking up Lolita's underclothes. Lolita is waiting at the lobby for Humbert to return.
\end{dida}

\hum%
Good morning, ma'am.

\custodian%
Good morning, sir. I was tidying up your room, and could not help noticing these \textit{ado-rable} girl clothes. Sir--- if I may ask, do you have a child with you?

\hum%
Why yes of \textit{course}, I am traveling with my daughter.

\custodian%
Your daughter! Some of these clothes look, oh--- a little racy, if you know what I mean, sir.

\hum[chuckling]
Well, she is going through her rebellious stage, and will only wear clothes she buys herself. It drives me \textit{mad}.

\custodian%
Oh, all teenagers do. Where is she?

\hum%
She is in the lobby, waiting for me to finish packing.

\custodian%
May I see her? I have a young boy too, but you know, he's off to the navy. Haven't seen him in \textit{years}! How I miss him!

\hum%
Ah, the navy--- a brave boy you have, indeed. Well, uh, my daughter is rather shy in front of strangers, and she doesn't like being stared at.

\custodian%
Ow, that's so very unfortunate. You know, sir, I haven't seen a young fellow in this god-awful place for so long. Most parents nowadays take their children to the city. How dreadful! God! I should've never said yes to my son. Leaving me like \textit{that}!

\hum%
I understand, ma'am. I, too, fear that one day Lo---my daughter---will escape--- I mean, leave me behind. An old man with nothing to treasure!

\custodian%
It is as if they have not felt any love from us, the old folks\dots when we've poured our whole darned hearts into them! I tell you, sir, parental love is the greatest love of all! 

\hum%
Well, yes, ma'am, I do agree. I love my daughter more than anything in the world. I love her dearly\dots as a father, of course. Yes. As a worried father. 

\hum% (Monologue)
Parental love is the greatest love of all? How ridiculous. If only this imbecile woman understood how \textit{I} feel about my Lo--- the light of my life, the fire of my loins! How could something as bland as parental love compare to \textit{my} love for her!

\custodian%
Oh, sir. I just wish these kids never grow up.

\hum%
I absolutely agree! Only if she can stay forever young and sweet, so I--- \did{pauses}

\custodian%
Sir?

\hum[smiling politely]
Never mind, ma'am. Thank you for your work, ma'am, here--- \did{handing the custodian some bills} I'm afraid I must go now. Can't keep her waiting!





\end{document}
